The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-08-20 sections/model.tex
Implement Irina's corrections in model part

Monthly temperature and precipitation are converted to surface accumulation and ablation by a temperature-index (positive degree-day) model. Ice accumulation is equal to precipitation when temperature is below 0\,\degC, and decreases linearly with temperature between 0 and 2\,\degC. Ice ablation is computed from the number of positive degree-days, defined as the integral of temperatures above 0\,\degC in one year. Positive degree-days are calculated by the \citet{calov-greve-2005} formula to accounts for day-to-day temperature variability by assuming a normal distribution along a central (input) value $T$:

@@

A positive degree-day model is a crude parametrization of physical processes occurring at a glacier's surface. Yet we believe that it captures reasonably accurate patterns of accumulation and ablation for our study area considering the employed climate data.

@@

Ice flow velocities are computed by a heuristic the Shallow Shelf Approximation (SSA) is used as a ``sliding law'' to a polythermal Shallow Ice Approximation (SIA) \citep{bueler-brown-2009}. Depth-averaged velocities $\vec{v}$ are computed as a weighted sum of SIA velocities $\vec{v_{\mathrm{SIA}}}$ and SSA velocities $\vec{v_{\mathrm{SSA}}}$ by

@@

SIA and SSA velocities are computed by finite difference methods on a 10km-resolution horizontal grid of 300 by 150 points. SIA velocities follow temperature-dependant creep. Temperatures are derived from an enthalpy formulation \citep{aschwanden-etal-2012} and computed in three dimensions on 51 irregularly spaced layers in ice and 11 regularly spaced layers in rock. An homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as lower boundary condition to the thermal model, and the surface air temperature from the various climate forcing is used as upper boundary condition.

SSA velocities are determined by a pseudo-plastic sliding law where the yield stress depends on the availability of basal water and a prescribed till friction angle$\phi$. We apply lower friction angles at low elevation to mimic the more slippery beds associated to the presence of marine sediments:

@@

With $\phi$ in degrees and $z$ in meters above present sea level. The glacier bed topography responds to the ice load following a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}.

>>>>

Monthly temperature and precipitation are converted to surface accumulation and ablation by a temperature-index (positive degree-day) model. Ice accumulation is equal to precipitation when temperature is below 0\,\degC, and decreases linearly with temperature between 0 and 2\,\degC. Ice ablation is computed from the number of positive degree-days, defined as the integral of temperatures above 0\,\degC in one year. Positive degree-days are calculated using the \citet{calov-greve-2005} formula to account for a day-to-day temperature variability by assuming a normal distribution along a central (input) value $T$:

@@

A positive degree-day model is a crude parametrization of physical processes occurring at a glacier's surface. Yet we believe that it captures reasonably accurately patterns of accumulation and ablation for our study area considering the employed climate data.

@@

Depth-averaged velocities $\vec{v}$ are computed as a weighted sum of Shallow Ice Approximation (SIA) velocities $\vec{v_{\mathrm{SIA}}}$ and Shallow Shelf Approximation (SSA) velocities $\vec{v_{\mathrm{SSA}}}$ \citep{bueler-brown-2009} by

@@

SIA and SSA velocities are computed by finite difference methods on a 10km-resolution horizontal grid of 300 by 150 points. SIA velocities follow temperature-dependent creep. Temperatures are derived from an enthalpy formulation \citep{aschwanden-etal-2012} and computed in three dimensions in 51 irregularly spaced layers in ice and 11 regularly spaced layers in bedrock. A homogeneous geothermal heat flux of 70\,\unit{W\,m^{-2}} is provided as a lower boundary condition to this composite thermal model, and the surface air temperature from various climate forcing is used as an upper boundary condition.

SSA velocities are determined by a pseudo-plastic sliding law where the yield stress depends on the availability of basal water and a prescribed till friction angle $\phi$. We apply lower friction angles at low elevation to mimic the more slippery beds associated to the presence of marine sediments:

@@

Where $\phi$ is given in degrees and $z$ in meters above the present sea level. The glacier bed topography responds to the ice load following a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}.
